Epilepsy example

### 2022-11-03 src/epil/epil.Rmd
Separate C++ for nu and epsilon are compiling now. The one together with a data flag still giving me trouble
epil_index now compiling (it doesn't like it when nu and epsilon are defined differently depending on the if statement)
Trying to do Laplace for epil with TMB

```{r}
fit7 <- tmbstan(obj = obj, chains = 4)
```

@@

>>>>

```{r}
fit7 <- tmbstan(obj = obj, chains = 4, refresh = 0)
```

@@

## Custom Laplace method with `aghq`

```{r}
compile("epil_index.cpp")
dyn.load(dynlib("epil_index"))
```

We're going to use a data structure to pass to `epil_index`.
A `toggle` value of `0` corresponds to `nu` and a toggle value of `1` corresponds to `epsilon`:

```{r}
index_controller <- data.frame(
  "toggle" = c(rep(0, dat$N * dat$J),  rep(1, dat$N)),
  "i" = c(1:(dat$N * dat$J), 1:dat$N)
)
```

We have already obtained the MAP estimate $\hat \theta$ in the `TMB` section above that we can use in our empirical Bayes procedure.

```{r}
opt_theta <- opt
```

Eventually create function of the form:

```{r}
xi_laplace_marginal <- function(i, opt_theta, finegrid) {
  #' To fill
}
```

Start with `i = 1` for the first marginal:

```{r}
i <- 1

#' I don't know if this is the right grid for this application...
fine_grid <- seq(-5, 5, length.out = 1000)

dat$toggle <- index_controller[i, "toggle"]
dat$i <- index_controller[i, "i"]

theta_names <- unique(names(opt_theta$par))
map_fixed_theta <- list()
param_fixed_theta <- param

for(theta in theta_names) {
  map_fixed_theta[[theta]] <- factor(NA)
  param[[theta]] <- opt_theta$par[[theta]]
}

#' Prepare the initialisation parameters if it's nu that we're toggling
if(dat$toggle == 0) {
  param_fixed_theta[["nu_i"]] <- param_fixed_theta$nu[i]
  param_fixed_theta[["nu_minus_i"]] <- param_fixed_theta$nu[-i]
  # param_fixed_theta$nu <- NULL
}

#' Or if it's epsilon that we're toggling
if(dat$toggle == 1) {
  param_fixed_theta[["epsilon_i"]] <- param_fixed_theta$epsilon[i]
  param_fixed_theta[["epsilon_minus_i"]] <- param_fixed_theta$epsilon[-i]
  # param_fixed_theta$epsilon <- NULL
}

get_random <- function(dat) {
  if(dat$toggle == 0) return(c("nu_minus_i", "epsilon"))
  if(dat$toggle == 1) return(c("nu", "epsilon_minus_i"))
}

obj_fixed_theta <- MakeADFun(
  data = dat,
  parameters = param_fixed_theta,
  random = get_random(dat),
  DLL = "epil_index",
  silent = TRUE,
  map = map_fixed_theta
)

quad <- aghq::aghq(
  ff = obj_fixed_theta,
  k = 3,
  startingvalue = 0,
  control = aghq::default_control_tmb()
)

pdf_and_cdf <- aghq::compute_pdf_and_cdf(quad, finegrid = finegrid)[[1]]

```
